Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
mathit for time

\newcommand{\match}{\mathit{match}}
\newcommand{\timeSlot}{\mathit{timeSlot}}
\newcommand{\state}{\mathit{state}}
\newcommand{\change}{\mathit{change}}
\newcommand{\totalChanges}{\mathit{totalChanges}}
\newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
\newcommand{\modMatch}{\mathit{modMatch}}
\newcommand{\position}{\mathit{position}}
\newcommand{\imbalance}{\mathit{imbalance}}
\newcommand{\maxImbalance}{\mathit{maxImbalance}}

@@

\noindent
We now take a temporal view (\ref{eq20}), such that $time[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a match, i.e. we channel between the match-perspective and the temporal-perspective.
%
% one dimensional time and decision variables
%
\begin{flalign}
    & \forall_{\tau \in [0..t-1]} ~ time[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
\end{flalign}

@@

Figure \ref{schedChanges} gives a pictorial view of the model, using the 7 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots. Again, top right, we give the schedule actually produced.  Middle left we have the $\match$ array and at the bottom the $time$ array. Above the $match$ array we have the $\modMatch$ array. The yellow arrows show the channeling between parts of the model.

\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats. The schedule is reproduced top right. On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $time$ and middle left the $\match$ array. The yellow arrows signify channeling between parts of the model.}
\label{schedChanges} 
\end{figure}

The decision variables are $time[{0}]$ to $time[{t-1}]$, i.e. for each time slot we decide what match takes place. A symmetry break is made at the top of search by forcing the first round to contain the matches (0,1), (2,3), ... i.e. $\forall_{i \in [0..m-1]} ~ \match[{2.i,2i+1}] = i$. The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.

@@

\noindent
We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision variables are $time[{0}]$ to $time[{t-1}]$ and the same symmetry breaking is imposed at top of search.

>>>>

\newcommand{\match}{\mathit{match}}
\newcommand{\timeSlot}{\mathit{timeSlot}}
\newcommand{\state}{\mathit{state}}
\newcommand{\change}{\mathit{change}}
\newcommand{\totalChanges}{\mathit{totalChanges}}
\newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
\newcommand{\modMatch}{\mathit{modMatch}}
\newcommand{\position}{\mathit{position}}
\newcommand{\imbalance}{\mathit{imbalance}}
\newcommand{\maxImbalance}{\mathit{maxImbalance}}
\newcommand{\timeVar}{\mathit{time}}

@@

We now take a temporal view (\ref{eq20}), such that $\timeVar[{\tau}]$ is a pair
$(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a
match, i.e. we channel between the match-perspective and the
temporal-perspective.
%
% one dimensional time and decision variables
%
\begin{flalign}
    & \forall_{\tau \in [0..t-1]} ~ \timeVar[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \timeVar[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
\end{flalign}

@@

Figure \ref{schedChanges} gives a pictorial view of the model, using the 7 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots. Again, top right, we give the schedule actually produced.  Middle left we have the $\match$ array and at the bottom the $\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The yellow arrows show the channeling between parts of the model.

\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats. The schedule is reproduced top right. On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $\timeVar$ and middle left the $\match$ array. The yellow arrows signify channeling between parts of the model.}
\label{schedChanges} 
\end{figure}

The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$, i.e. for each time slot we decide what match takes place. A symmetry break is made at the top of search by forcing the first round to contain the matches (0,1), (2,3), ... i.e. $\forall_{i \in [0..m-1]} ~ \match[{2.i,2i+1}] = i$. The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.

@@

\noindent
We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
